\mireval{}

### 2014-05-08 paper/paper.tex
Bad ref
Chord rec -> chord est

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.

@@

For the beat detection, chord recognition, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
We chose to compare against the results reported in MIREX 2013 for all tasks.

@@

\begin{table*}[htb]
\label{tab:comparison}
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\end{table*}

@@

\subsection{Weighted Chord Symbol Recall}
For reference, we compare our chord evaluation against the results provided from MIREX 2013.
Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{table:comparisons}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.

>>>>

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord estimation systems.
One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.

@@

For the beat detection, chord estimation, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
We chose to compare against the results reported in MIREX 2013 for all tasks.

@@

\begin{table*}[htb]
\label{tab:comparison}
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{Chord Estimation} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\end{table*}

@@

\subsection{Weighted Chord Symbol Recall}
For reference, we compare our chord evaluation against the results provided from MIREX 2013.
Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.
